INTELLIGENT SYSTEMS

### 2021-03-31 paper_3.tex
finish 3.4.2

>>>>

\subsection{EXPERIMENTS}
In order to evaluate the performance of the proposed framework, the results 
obtained were compared with six deblocking methods and two denoising 
methods. In order to train the network, the \emph{MatConvNet} \cite{0799924138} package is 
used.

\subsubsection{Datasets for Training and Testing}
For training, 400 images of 180x180 size are used. The patches used are in 
total 204800 $ (400x8x64)^2 $, with stride equal to 20. For the test, however only 
7 images are used which obviously are not present in the training ones.

\subsubsection{Model Initialization}
The initialization of the weights takes place following the method in \cite{0799924140}, 
while for the optimization of the gradient the method defined in \cite{0799924121} is used.
The training of the ComCNN network takes place in 50 epochs with a batch 
size of 128. The learning rate falls from 0.01 to 0.0001. The initial parameters 
of the second RecCNN network are identical to those of the first network, 
including the batch size.
